Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added description of "grouping buildings based on buffering"

\subsection{Simplification}
We use an offset-based method, similar to \textcite{Damen2008,Meijers2016}, to 
simplify our grown buildings. We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

@@

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on C\# (Microsoft Visual 
Studio 
2015) and ArcObjects SDK \revise{for the Microsoft .Net Framework}{}10.2. 
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
%As ArcObjects SDK for the Microsoft .Net Framework 10.2 can 
%only  run under a 32-bit platform, we set a Post-build 
%event\footnote{The details of the setting can be found at 	
%\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio}.},
%in Microsoft Visual Studio 2012
%so that we managed to use up to 3GM of RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
We tested our method on a dataset from the German topographic 
database ATKIS DLM 50. The dataset represents the place 
``Buchholz in der Nordheide'' at scale $1:50{,}000$. Our start 
map is the map after the collapse of areas by \citet[pp. 
61--66]{haunert2008f}, which has $5{,}537$ polygons. Our goal 
map was generalized from the start map by 
\citet{haunertwolff2010b} setting the scale at $1:250{,}000$ 
(see Fig.~\ref{fig:Data}). The goal map has $734$ polygons, 
which means that \revise{we have}{there are $N=734$} regions.

@@

>>>>

\subsection{Grouping buildings based on buffering}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
where distance $d_G$ is the growing amount of each building. 
Parameter $d_\epsilon$ is the least distance allowed between two buildings.
We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
the corresponding two buildings will become too close during our growing step.
The two buildings are in the same group.

We merge the buffers which overlap each others so that we have some large units.
Now we iteratively remove small ``bays''.
Each iteration consists of three steps, i.e., 
buffering with distance $r_H$, buffering with distance $-r_H$, and
merging overlapping units.
The iterative process stops when the number of units do not decrease anymore.

All the buildings overlapping with the same unit belong to the same group.

\subsection{Enlarging and merging buildings}

\subsection{Simplifying merged buildings}
We use an buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

@@

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on C\# (Microsoft Visual 
Studio 
2015) and ArcObjects SDK 10.4.1. 
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
We tested our method on a dataset from French Mapping Agency (IGN).
The dataset represents four towns (communes in French), i.e., Aussevielle, 
Denguin,  Poey-de-Lescar, and Siros, in the 
Pyr\'en\'ees-Atlantiques department, south-western France.
The scale of the dataset is $1:15{,}000$.
Our goal scale is $1:50{,}000$.

@@

We did not include streets. We can either put them above the settlement 
boundaries on map, or use them as restriction for building growing.
